\declarefields{nome,rg,minicurso1,minicurso2}

\newcommand{\defineasentradas}[4]{\newentry{{#1},{#2},{#3},{#4}}}

\defineasentradas
{Murillo PachÍco Cabral}  {4154031 DGPC-GO}  {MAQUETE ELETRÙNICA}  {MONT. E MANUT. PC}


\defineasentradas
{Luciana de Oliveira Pereira}  {4278282 DGPC-GO}  {LATEX}  {DIMEN DE LAJES PRÈ-MOLDADAS}


\defineasentradas
{Guilherme Limeira Santana}  {4624636 SSP-GO}  {PLANILHA ELETRÙNICA}  {MONT. E MANUT. PC}


\defineasentradas
{Thayse Lacerda Le„o}  {4513875 SSP-GO}  {MAQUETE ELETRÙNICA}  {MONT. E MANUT. PC}


\defineasentradas
{S·vio Souza Costa}  {4296427 DGPC-GO}  { DIMEN DE LAJES PRÈ-MOLDADAS }  {MONT. E MANUT. PC}


\defineasentradas
{Ludy Carrijo Soares}  {4308072 DGPC-GO}  {EMPREENDORISMO}  {DIMEN DE LAJES PRÈ-MOLDADAS}


\defineasentradas
{Jo„o Augusto Milhomens de Moura}  {4522894 DGPC-GO}  {EMPREENDORISMO}  {PLANILHA ELETR‘NICA}


\defineasentradas
{Marcelo Vieira Baptista}  {4569226 DGPC-GO}  {EMPREENDORISMO}   {DIMEN DE LAJES PR…-MOLDADAS}


\defineasentradas
{Silvio LourenÁo da Silva Filho}  {4536185 DGPC-GO}  {DIMEN DE LAJES PR…-MOLDADAS}  {MONT. E MANUT. PC}


\defineasentradas
{AurÈlio Augusto Cunha}  {4624978 DGPC-GO}  {MAQUETE ELETR‘NICA}  {DIMEN DE LAJES PR…-MOLDADAS}


\defineasentradas
{Gisela de Souza Ribeiro}  {5237761 SPTC-GO}  {MAQUETE ELETR‘NICA}  {DIMEN DE LAJES PR…-MOLDADAS}


\defineasentradas
{Rodrigo Rodrigues Toledo}  {4500645 SSP-GO}  {EMPREENDORISMO}  {DIMEN DE LAJES PR…-MOLDADAS}


\defineasentradas
{Leife Thomaz de Cantu·ria}  {4060806 DGPC-GO}  {DIMEN DE LAJES PR…-MOLDADAS}  {MONT. E MANUT. PC}



\defineasentradas
{Edson Tejerina CalderÛn}  {}  {CALC HP PARA INICIANTES}  {SAP}



